The Socialization of Meritocracy: The role of the Family and the School

### 2023-06-07 docs/presentacion-effort/presentation-effort.Rmd
typos

.pull-left-narrow[
# **PRICE**:
### Programa de Investigación en Ciudadanía Escolar
]

@@

  - Intergenerational transmission of beleifs and attitudes (socialisation)

>>>>

.pull-left-narrow[
# **PRICE**:
### Programa de Investigación en Ciudadanía Escolar
(School Citizenship Research Programme)
]

@@

  - Intergenerational transmission of beliefs and attitudes (socialisation)
